Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/empirical-comparison.tex
Add reference to Francesco's source code

We implemented
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
Algorithm~\ref{algorithm:kernelized} with rational
kernel~\eqref{equation:rational-kernel}, and the \textsc{Banditron} algorithm.
We evaluated these algorithms on the two datasets. \textsc{Banditron} has an
exploration rate parameter, for which we tried values $0.02, 0.01, 0.005, 0.002,
0.001, 0.0005$. Since all three algorithms are randomized, we run each algorithm
$20$ times. The average cumulative number of mistakes up to round $t$ as a
function of $t$ are shown in
Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
and~\ref{figure:number-of-mistakes-weakly-separable-dataset}.

>>>>

We implemented
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples},
Algorithm~\ref{algorithm:kernelized} with rational
kernel~\eqref{equation:rational-kernel} and used implementation of
\textsc{Banditron} algorithm by \citet{Orabona09}.\footnote{All the source code
is included in the supplementary material.}
We evaluated these algorithms on the two datasets. \textsc{Banditron} has an
exploration rate parameter, for which we tried values $0.02, 0.01, 0.005, 0.002,
0.001, 0.0005$. Since all three algorithms are randomized, we run each algorithm
$20$ times. The average cumulative number of mistakes up to round $t$ as a
function of $t$ are shown in
Figures~\ref{figure:number-of-mistakes-strongly-separable-dataset}
and~\ref{figure:number-of-mistakes-weakly-separable-dataset}.
